Estimating duration in the presence of misclassification

### 2023-12-20 biology-data.tex
Outline intro

@@

@@

>>>>

\section{Natural history of the disease}

Possible summaries
\begin{enumerate}
  \item \url{https://www.nature.com/articles/s41579-022-00822-w/figures/2}
  \item \url{https://www.nature.com/articles/s41576-021-00360-w/figures/1}
  \item \url{https://academic.oup.com/view-large/figure/305617142/ciaa1442_fig2.jpg}
\end{enumerate}

\begin{itemize}
  \item Phases: pre-infection positive, infectious positive, post-infectious positive, negative
  \item Relationship between different means of infected: infectious, PCR positive, symptomatic/diseased
\end{itemize}

@@

\emph{Describe how PCR testing works}

@@

\subsubsection{Episodes}

\emph{Explain definition in ``SARS-CoV-2 reinfection definition'' from \textcite{weiRisk}.}

### 2023-12-20 introduction.tex
Outline intro

@@

\begin{itemize}
    \item Double interval censoring with arbitrary truncation and false negatives
    \item Combining ATACCC and CIS duration estimates
    \item SEIR model using only prevalence surveys
    \item Application within TRE
\end{itemize}

>>>>

- Natural history of SARS-CoV-2 infection
	- Stylised graphic of phases: infection, pre-infection positive, infectious positive, post-infectious positive, negative
	- How it spreads
- Why is incidence and prevalence estimation challenging?
	- Asymptomatic infection
	- Ascertainment bias
- How do we estimate prevalence
	- CIS and REACT
- Issues with current incidence estimation

@@

\begin{itemize}
    \item Theory justifying the use of deterministic backcalculation in this setting. Already used in practice but without understanding when the approximation is good. In particular: all that is required is that the proportion of the population sampled is small, not that the prevalence or incidence is sufficiently large.
    \item Double interval censoring with arbitrary truncation and false negatives
    \item Combining ATACCC and CIS duration estimates
    \item SEIR model using only prevalence surveys
    \item Application within TRE
\end{itemize}
